---
title: "Developing Data Products Week 4 Assignment"
author: "Sandeep Rangarajen"
date: "21/02/2022"
output:
  slidy_presentation: default
  ioslides_presentation: default
  beamer_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## This is the "Developing Data Products Week 4 Assignment" and is part of the Data Science Certification programme

## <span style="color:blue">First Objective</span>:

The files are available at Github repository https://github.com/sandeeprangarajen/DD4_Week_4_Assignment


## <span style="color:blue">Second Objective</span>:

The presentation is available at Rpubs https://rpubs.com/sandeeprangarajen/869237

## Introduction

Background, History and Updates:
The basic GISS temperature analysis scheme was defined in the late 1970s by James Hansen when a method of estimating global temperature change was needed for comparison with one-dimensional global climate models

The following data set have been downloaded from the site


Global-mean monthly, seasonal, and annual means, 2002-present, updated through most recent month: TXT, CSV

Northern Hemisphere-mean monthly, seasonal, and annual means, 2002-present, updated through most recent month: TXT, CSV

Southern Hemisphere-mean monthly, seasonal, and annual means, 2002-present, updated through most recent month: TXT, CSV

## Dataset

https://data.giss.nasa.gov/gistemp/tabledata_v4/GLB.Ts+dSST.csv

https://data.giss.nasa.gov/gistemp/tabledata_v4/NH.Ts+dSST.csv

https://data.giss.nasa.gov/gistemp/tabledata_v4/SH.Ts+dSST.csv

<span style="color:blue">Printing sample 10 rows of Global Data file</span>:
```{r cars}
GlobalData <- read.csv("./data/GLBTs_dSST.csv", sep = ',', stringsAsFactors = TRUE)
NorthPoleData <- read.csv("./data/NHTs_dSST.csv", sep = ',', stringsAsFactors = TRUE)
SouthPoleData <- read.csv("./data/SHTs_dSST.csv", sep = ',', stringsAsFactors = TRUE)
GlobalData[1:10, ] 
```

## Application

URL for Shiny application is http://127.0.0.1:3004

The Application contains :

<span style="color:blue">**Left Pane**</span>:

- Select data options using radio buttons from North Pole, South Pole or Global Data
- Select Year Range using Slider Range. Data Range contains minimum year as 2002 and maximum year as 2022.
- Select Variable from Data set. This is a multiple selection text field which contains months from January to December.



<span style="color:blue">**Main Panel**</span>

There are four panes in main panel as below :

- <span style="color:red">**Summary**</span> : This displays Summary for the data as per user selection.

- <span style="color:red">**Structure**</span> : This displays Structure for the data as per user selection.

- <span style="color:red">**Data**</span> : This displays Data Frame for the user selected options.

- <span style="color:red">**Plot**</span>: : This displays plot for corresponding data frame
